A pipeline to analyse time-course gene expression data

### 2020-07-22 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

The manuscript was last compile on 2020-07-21 12:22:19.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{cluster_of_interest =}\StringTok{ }\DecValTok{2}
\NormalTok{cluster2Genes =}\StringTok{ }\KeywordTok{names}\NormalTok{(}
\NormalTok{    kmeans_clusters}\OperatorTok{$}\NormalTok{clusters[kmeans_clusters}\OperatorTok{$}\NormalTok{clusters}\OperatorTok{==}\NormalTok{cluster_of_interest])}
\CommentTok{# }\AlertTok{FIXME}\CommentTok{ This line fails}
\CommentTok{# dataToPlot = rbind(}
\CommentTok{#     assay(de_moanin_model[cluster2Genes[3:6],]), }
\CommentTok{#    "Centroid"=kmeans_clusters$centroids[cluster_of_interest,])}
\CommentTok{# plot_splines_data(de_moanin_model, data=dataToPlot, }
\CommentTok{#     colors=ann_colors$Group, smooth=TRUE, simpleY=FALSE,}
\CommentTok{#    mar=c(1.5,2.5,2,0.1))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# order them by their score in cluster}
\NormalTok{ord =}\StringTok{ }\KeywordTok{order}\NormalTok{(scores_and_labels}\OperatorTok{$}\NormalTok{scores[genes_in_cluster2,}
\NormalTok{                     cluster_of_interest])}
\NormalTok{cluster2Score =}\StringTok{ }\NormalTok{genes_in_cluster2[ord]}
\CommentTok{# }\AlertTok{FIXME}\CommentTok{ this lines failes.}
\CommentTok{# dataToPlot = rbind(assay(moanin_model[cluster2Score[1:4], ]),}
\CommentTok{#     "Centroid"=kmeans_clusters$centroids[cluster_of_interest, ])}
\CommentTok{# plot_splines_data(moanin_model, data=dataToPlot, }
\CommentTok{#     colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,}
\CommentTok{#     mar=c(1.5,2.5,2,0.1))}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# Now use the results of the previous call to aheatmap to reorder the genes.}
\CommentTok{# }\AlertTok{FIXME}\CommentTok{ this line doesn't work}
\CommentTok{# aheatmap(}
\CommentTok{#    rescale_values(moanin_model[genes_to_plot,ord])[res$rowInd,],}
\CommentTok{#    Colv=NA,}
\CommentTok{#    Rowv=NA,}
\CommentTok{#    annCol=orderedMeta[, c("Group", "Timepoint")],}
\CommentTok{#    annLegend=TRUE,}
\CommentTok{#    annColors=ann_colors,}
\CommentTok{#    main=paste("Cluster", cluster_to_plot, "(rescaled)"),}
\CommentTok{#    treeheight=0)}
\end{Highlighting}
\end{Shaded}

@@

##  [3] ggfortify_0.4.10            timecoursedata_0.99.0      

>>>>

The manuscript was last compile on 2020-07-22 10:25:43.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{cluster_of_interest =}\StringTok{ }\DecValTok{2}
\NormalTok{cluster2Genes =}\StringTok{ }\KeywordTok{names}\NormalTok{(}
\NormalTok{    kmeans_clusters}\OperatorTok{$}\NormalTok{clusters[kmeans_clusters}\OperatorTok{$}\NormalTok{clusters}\OperatorTok{==}\NormalTok{cluster_of_interest])}
\NormalTok{dataToPlot =}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}
    \KeywordTok{assay}\NormalTok{(de_moanin_model[cluster2Genes[}\DecValTok{3}\OperatorTok{:}\DecValTok{6}\NormalTok{],]), }
    \StringTok{"Centroid"}\NormalTok{=kmeans_clusters}\OperatorTok{$}\NormalTok{centroids[cluster_of_interest,])}
\KeywordTok{plot_splines_data}\NormalTok{(de_moanin_model, }\DataTypeTok{data=}\NormalTok{dataToPlot, }
    \DataTypeTok{colors=}\NormalTok{ann_colors}\OperatorTok{$}\NormalTok{Group, }\DataTypeTok{smooth=}\OtherTok{TRUE}\NormalTok{, }\DataTypeTok{simpleY=}\OtherTok{FALSE}\NormalTok{,}
    \DataTypeTok{mar=}\KeywordTok{c}\NormalTok{(}\FloatTok{1.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{,}\DecValTok{2}\NormalTok{,}\FloatTok{0.1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=.5\textwidth,]{reports/manuscript_files/figure-latex/genesVsCentroids-1} \end{center}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# order them by their score in cluster}
\NormalTok{ord =}\StringTok{ }\KeywordTok{order}\NormalTok{(scores_and_labels}\OperatorTok{$}\NormalTok{scores[genes_in_cluster2,}
\NormalTok{                     cluster_of_interest])}
\NormalTok{cluster2Score =}\StringTok{ }\NormalTok{genes_in_cluster2[ord]}
\NormalTok{dataToPlot =}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{assay}\NormalTok{(moanin_model[cluster2Score[}\DecValTok{1}\OperatorTok{:}\DecValTok{4}\NormalTok{], ]),}
    \StringTok{"Centroid"}\NormalTok{=kmeans_clusters}\OperatorTok{$}\NormalTok{centroids[cluster_of_interest, ])}
\KeywordTok{plot_splines_data}\NormalTok{(moanin_model, }\DataTypeTok{data=}\NormalTok{dataToPlot, }
     \DataTypeTok{colors=}\NormalTok{ann_colors}\OperatorTok{$}\NormalTok{Group, }\DataTypeTok{smooth=}\OtherTok{TRUE}\NormalTok{,}\DataTypeTok{simpleY =}\OtherTok{FALSE}\NormalTok{,}
     \DataTypeTok{mar=}\KeywordTok{c}\NormalTok{(}\FloatTok{1.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{,}\DecValTok{2}\NormalTok{,}\FloatTok{0.1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=.5\textwidth,]{reports/manuscript_files/figure-latex/topScoreInCluster2-1}

\caption{Top scoring genes in Cluster 2}\label{fig:topScoreInCluster2}
\end{figure}

@@

\CommentTok{# Now use the results of the previous call to aheatmap to reorder the genes.}
\KeywordTok{aheatmap}\NormalTok{(}
    \KeywordTok{rescale_values}\NormalTok{(moanin_model[genes_to_plot,ord])[res}\OperatorTok{$}\NormalTok{rowInd,],}
    \DataTypeTok{Colv=}\OtherTok{NA}\NormalTok{,}
    \DataTypeTok{Rowv=}\OtherTok{NA}\NormalTok{,}
    \DataTypeTok{annCol=}\NormalTok{orderedMeta[, }\KeywordTok{c}\NormalTok{(}\StringTok{"Group"}\NormalTok{, }\StringTok{"Timepoint"}\NormalTok{)],}
    \DataTypeTok{annLegend=}\OtherTok{TRUE}\NormalTok{,}
    \DataTypeTok{annColors=}\NormalTok{ann_colors,}
    \DataTypeTok{main=}\KeywordTok{paste}\NormalTok{(}\StringTok{"Cluster"}\NormalTok{, cluster_to_plot, }\StringTok{"(rescaled)"}\NormalTok{),}
    \DataTypeTok{treeheight=}\DecValTok{0}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

##  [3] ggfortify_0.4.10            timecoursedata_0.99.13     
